A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2021-03-11 04_Severity_MetaAnalysis.Rmd
Wordsmithing and output contrasts to a flextable

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr,
               flextable)

@@

Inspect for a normal distribution of disease severity
```{r sev_hist}
hist(PM_dat_D$PM_final_severity)
```

Let's get started with the analysis by first finding the best model fit that answers our research question.

> When, in relation to PM establishment in the crop, should farmers begin spraying mungbean to obtain the highest fungicide efficacy for lowering disease severity: before PM establishing,  immediately after first sign of PM establishing, or after PM has become established in the crop.

A secondary question to this aim is: does a second spray increase the efficacy?

To do this, in our model:

   - Powdery mildew severity 1-9 scale

   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept

@@

   - We will investigate the effect size of our treatment - spray management,

<br>  
<br>  
<br>  
******

@@

All spray schedules were effective at lowering the disease severity at the end of the season

@@

@@

contrast_Ssum
```

@@

@@

Save table to a word document to use in manuscript
```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = disease_estimates_table)
print(doc, target = "paper/figures/Table3_severity_esimates.docx")
```

>>>>

An additional question to our main aim: does spray schedule have a similar effect on disease severity?

This model will be similar to the grain yield meta-analysis and use the main variables:

   - *Powdery mildew severity* the response variable (1-9 scale)

   - *Trial*, which resolves combinations of categorical random variables: 
      i) year  
      ii) location  
      iii) row spacing  
      iv) cultivar

   - *spray_management* a moderator to evaluate the difference in effect size attributed to fungicide application timing.

   - *id* random variable indicating each treatment is independent

<br>

Load libraries and data  
```{r MEsummary_Libraries2, echo=TRUE,results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr,
               flextable)

@@

<br>  
<br>

@@

Inspect disease severity for a normality.
```{r sev_hist}
hist(PM_dat_D$PM_final_severity)
```

*****

@@

All spray schedules were effective at lowering the disease severity at the end of the season.
`Recommended_plus` reduced powdery mildew incidence the most.

@@

Calculate the treatment contrasts

@@

contrast_Ssum %>%
   flextable()
```

@@

`Recommended_plus` limited disease severity significantly better than any other spray treatment. 
`Late_plus` limited disease severity significantly better than a single `Late` application. 
This indicates that two spray treatments were significantly better than a single application, but the timing of the fungicide application was more critical.

@@

```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = disease_estimates_table)
print(doc, target = "paper/figures/Table3_severity_esimates.docx")
```
